The Privacy of Private Browsing

### 2013-12-14 finalproject/paper.tex
started adding specific browser flaws

    \singlespacing
    \begin{center}
      \begin{tabular}{|p{5cm}|c|c|c|}
        \hline
         & Firefox & Chrome & Internet Explorer \\
         & Private Browsing & Incognito Mode & InPrivate Browsng \\
        \hline
        Browser history & X & X & X \\
        \hline
        Form data & X &  & X \\
        \hline
        Search bar data & X &  & X \\
        \hline
        Passwords & X &  & X \\
        \hline
        Downloads & X & X &  \\
        \hline
        Cookies & X & X & X \\
        \hline
        Cached files & X &  & X \\
        \hline
        Simulataneous sessions with different privacy settings & X & X & X \\
        \hline
      \end{tabular}
    \end{center}
    \doublespacing

	\subsection{Definitions}
	Many shortcomings of private browsing modes relate to how a computer's 
	operating system manages memory and disk space. Those who are unfamiliar
	with these tasks may benefit from the definitions below.

	\begin{description}
	  \item[Cluster] A group of disk sectors that the operating system
	  treats as a unit; smallest unit of disk storage that the operating
	  system can allocate
	  \item[Disk] The hard drive of a computer; where a user's files and
	  directories (among other things) are stored
	  \item[Free space] A cluster that is not allocated to any particular 
	  file
	  \item[Page] The smallest unit of memory that the operating system can
	  allocate; can be temporarily stored on disk to allow the computer to run
	  more programs at the same time
	  \item[Slack space] The space between the end of a file and the end of 
	  the cluster in which it is stored; important in computer forensics for
	  finding fragments of old files\footnote{Hard drive clusters are of a 
	  fixed size determined by the operating system. Most of the time, when a 
	  user saves a file to his or her hard drive, the file is not exactly the 
	  same size as the cluster in which the operating system puts it. 
	  Furthermore, when a user ``deletes'' a file from his or her hard drive, 
	  the file is not really deleted---it is simply marked as available to be
      overwritten if necessary. If a file is eventually stored on the hard 
	  drive in a cluster that used to be home to a larger (now ``deleted'') 
	  file, leftover data from the old file will still exist at the end of that
      cluster.}
	\end{description}

@@

    \subsection{Where To Look}
    Focused analysis of the hard drive itself can reveal the most artifacts.
    One private browsing experiment in which logon information, browser
    history, and cached images were recovered obtained most of the artifacts
    from the hard drive's free space and slack space.\cite{ohana13}

@@

    The Windows pagefile can also reveal private browsing artifacts. This file
    is where the least recently used pages of memory are stored when too many
    applications are competing for the computer's physical memory. Browsing
    history and keywords used in internet search engines have been discovered
    here.\cite{said11}

    \subsection{Firefox}
	In 2011, researchers discovered that Firefox 3.6.11 stored browser history
	and search engine keywords in the computer's physical memory and that this
	information could be accessed after the browsing session was terminated.
	An analysis of the contents of pagefile.sys revealed similar information.
	\cite{said11} Additionally, certificate chains received during private 
	browsing sessions in Firefox 3.6 were not removed from their on-disk 
	database once the browsing session was terminated.

    \subsection{Google Chrome}

    \subsection{Internet Explorer}
    Internet Explorer leaves the most artifacts behind when its InPrivate
    Browsing mode terminates.\cite{ohana13}

@@

  \singlespacing
  \begin{thebibliography}{9}
    \bibitem{verdi13}
      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
      without-saving-info}$>$.
    \bibitem{google13}
      ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.google.com/intl/en/chrome/browser/
      features.html#privacy}$>$.
    \bibitem{ie13}
      ``InPrivate Browsing.'' \emph{Microsoft Windows}. Microsoft, 10 Dec. 
      2013. Web. 10 Dec. 2013. $<$\url{http://windows.microsoft.com/en-us/
      internet-explorer/products/ie-9/features/in-private}$>$.
    \bibitem{tor13}
      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$. 
    \bibitem{ohana13}
      Ohana, Donny, and Narasimha Shashidhar. ``Do Private and Portable Web 
      Browsers Leave Incriminating Evidence? A Forensic Analysis of Residual 
      Artifacts from Private and Portable Web Browsing Sessions.'' IEEE CS 
      Security and Privacy Workshops (SPW), The Westin St. Francis, 
      San Francisco, CA. 23-24 May 2013. Web. 9 Dec. 2013. $<$\url{http://www.
      ieee-security.org/TC/SPW2013/papers/data/5017a135.pdf}$>$
    \bibitem{satvat13}
      Satvat, Kiavash, Matthew Forshaw, Feng Hao, and Ehsan Toreini. ``On The 
      Privacy of Private Browsing - A Forensic Approach.'' Proceedings of the 
      8th International Workshop on Data Privacy Management (DPM '13), Royal 
      Holloway, University of London, Egham, UK. 12-13 Sept. 2013. Web. 9 Dec.
      2013. $<$\url{http://homepages.cs.ncl.ac.uk/feng.hao/files/DPM13.pdf}$>$ 
    \bibitem{said11}
      Said, Huwida, Noora Al Mutawa, Ibtesam Al Awadhi, and Mario Guimaraes.
      ``Forensic Analysis of Private Browsing Artifacts.'' 7th International
      Conference on Innovations in Information Technology, Abu Dhabi, United
      Arab Emirates. 25-27 Apr. 2011. Web. 10 Dec. 2013. $<$\url{http://
      ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=&arnumber=5893816}$>$

  \end{thebibliography}

\end{document}

>>>>

    \singlespacing
    \begin{center}
      \begin{tabular}{|p{5cm}|c|c|c|}
        \hline
         & Firefox & Chrome & Internet Explorer \\
         & Private Browsing & Incognito Mode & InPrivate Browsng \\
        \hline
        Browser history & X & X & X \\
        \hline
        Form data & X &  & X \\
        \hline
        Search bar data & X &  & X \\
        \hline
        Passwords & X &  & X \\
        \hline
        Downloads & X & X &  \\
        \hline
        Cookies & X & X & X \\
        \hline
        Cached files & X &  & X \\
        \hline
        Simulataneous sessions with different privacy settings & X & X & X \\
        \hline
      \end{tabular}
    \end{center}

    \doublespacing
	\subsection{Definitions}
	Many shortcomings of private browsing modes relate to how a computer's 
	operating system manages memory and disk space. Those who are unfamiliar
	with these tasks may benefit from the definitions below.

	\begin{description}
	  \item[Cluster] A group of disk sectors that the operating system
	  treats as a unit; smallest unit of disk storage that the operating
	  system can allocate
	  \item[Digital certificate] Verifies that a particular website or target
	  server is who it claims to be when connecting securely
	  \item[Disk] The hard drive of a computer; where a user's files and
	  directories (among other things) are stored
	  \item[Free space] A cluster that is not allocated to any particular 
	  file
	  \item[Page] The smallest unit of memory that the operating system can
	  allocate; can be temporarily stored on disk to allow the computer to run
	  more programs at the same time
	  \item[Slack space] The space between the end of a file and the end of 
	  the cluster in which it is stored; important in computer forensics for
	  finding fragments of old files\footnote{Hard drive clusters are of a 
	  fixed size determined by the operating system. Most of the time, when a 
	  user saves a file to his or her hard drive, the file is not exactly the 
	  same size as the cluster in which the operating system puts it. 
	  Furthermore, when a user ``deletes'' a file from his or her hard drive, 
	  the file is not really deleted---it is simply marked as available to be
      overwritten if necessary. If a file is eventually stored on the hard 
	  drive in a cluster that used to be home to a larger (now ``deleted'') 
	  file, leftover data from the old file will still exist at the end of that
      cluster.}
	\end{description}

@@

    \subsection{Where To Look}
    Focused analysis of the hard drive can reveal the most artifacts.
    One private browsing experiment in which logon information, browser
    history, and cached images were recovered obtained most of the artifacts
    from the hard drive's free space and slack space.\cite{ohana13} The 
	Windows pagefile (pagefile.sys on the hard drive) in particular can reveal
	private browsing artifacts. This file is where the least recently used 
	pages of memory are stored when too many applications are competing for the
	computer's physical memory. Browsing history and keywords used in internet 
	search engines have been discovered here.\cite{said11}

@@

    \subsection{Firefox}
	In 2011, researchers discovered that Firefox 3.6.11 stored browser history
	and search engine keywords in the computer's physical memory and that this
	information could be accessed after the browsing session was terminated.
	An analysis of the contents of pagefile.sys revealed similar information.
	\cite{said11} Additionally, digital certificates received during private 
	browsing sessions in Firefox 3.6 were not removed from their on-disk 
	database once the browsing session was terminated.\cite{aggarwal10}

    \subsection{Google Chrome}
    One 2013 study stated that it was more difficult to retrieve private
	browsing artifacts from Chrome's incognito mode than Firefox or Internet
	Explorer.\cite{said11}

    \subsection{Internet Explorer}
    Internet Explorer leaves the most artifacts behind when its InPrivate
    Browsing mode terminates.\cite{ohana13} Internet Explorer 8.0.6001.18702
	continued to cache web pages on the hard drive during an InPrivate
	Browsing session, but these files were deleted once the browser window was
	closed. This means that fragments of these files---and thus a record of the
	user's browsing history---could be discovered by analyzing the free and
	slack space of the hard drive.\cite{said11}

@@

  \singlespacing
  \begin{thebibliography}{9}
	\bibitem{aggarwal10}
	  Aggarwal, Gaurav, Elie Bursztein, Collin Jackson, and Dan Boneh.
	  ``An Analysis of Private Browsing Modes in Modern Browsers.''
	  Proceedings of the 19th USENIX Security Symposium,  Wardman Park Marriott
	  Hotel, Washington, D.C. 11-13 Aug. 2013. Web. 8 Dec. 2013. $<$
	  \url{http://crypto.stanford.edu/~dabo/pubs/papers/privatebrowsing.pdf}$>$
    \bibitem{google13}
      ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.google.com/intl/en/chrome/browser/
      features.html#privacy}$>$.
    \bibitem{ie13}
      ``InPrivate Browsing.'' \emph{Microsoft Windows}. Microsoft, 10 Dec. 
      2013. Web. 10 Dec. 2013. $<$\url{http://windows.microsoft.com/en-us/
      internet-explorer/products/ie-9/features/in-private}$>$.
    \bibitem{ohana13}
      Ohana, Donny, and Narasimha Shashidhar. ``Do Private and Portable Web 
      Browsers Leave Incriminating Evidence? A Forensic Analysis of Residual 
      Artifacts from Private and Portable Web Browsing Sessions.'' IEEE CS 
      Security and Privacy Workshops (SPW), The Westin St. Francis, 
      San Francisco, CA. 23-24 May 2013. Web. 9 Dec. 2013. $<$\url{http://www.
      ieee-security.org/TC/SPW2013/papers/data/5017a135.pdf}$>$
    \bibitem{said11}
      Said, Huwida, Noora Al Mutawa, Ibtesam Al Awadhi, and Mario Guimaraes.
      ``Forensic Analysis of Private Browsing Artifacts.'' 7th International
      Conference on Innovations in Information Technology, Abu Dhabi, United
      Arab Emirates. 25-27 Apr. 2011. Web. 10 Dec. 2013. $<$\url{http://
      ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=&arnumber=5893816}$>$ 
    \bibitem{satvat13}
      Satvat, Kiavash, Matthew Forshaw, Feng Hao, and Ehsan Toreini. ``On The 
      Privacy of Private Browsing - A Forensic Approach.'' Proceedings of the 
      8th International Workshop on Data Privacy Management (DPM '13), Royal 
      Holloway, University of London, Egham, UK. 12-13 Sept. 2013. Web. 9 Dec.
      2013. $<$\url{http://homepages.cs.ncl.ac.uk/feng.hao/files/DPM13.pdf}$>$ 
	\bibitem{tor13}
      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$. 
	\bibitem{verdi13}
      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
      without-saving-info}$>$.
  \end{thebibliography}
\end{document}
